### 2019-03-05 manuscript.tex
small updates to manuscript and notebook

In the paleogeographic model framework of Pehrsson et al. (2015), the cratonic and terrane collisions leading up to the Trans-Hudson orogeny mark the initial phase of assembly of the supercontinent Nuna. The Trans-Hudson orogeny itself is taken to be the terminal collision associated with the closure of the Manikewan Ocean that had previous been a large oceanic tract separating the Superior craton from the composite Slave+Rae+Hearne+Nain cratons (often referred to as the Churchill domain or plate; e.g. Skipton et al., 2016; Weller and St-Onge, 2017). This model posits that this period terminal collision is not only associated with the amalgmation of Laurentia, but is also associated with the assembly of the supercontinent Nuna that including other major Paleoproterozoic cratons including Siberia, Congo/Sao Francisco, West Africa, and Amazonia (Pehrsson et al., 2015). Following the Trans-Hudson orogeny, the locus of orogenesis migrated to the exterior of Laurentia. This change marks a change in the style of Laurentia's growth as subsequent growth proceeding dominantly through accretion of juvenile crust along the southern and eastern margin of the nucleus of Archean cratons (Whitmeyer and Karlstrom, 2007; \ref{fig:Laurentia_map}).

@@

\begin{figure}
\centering
\includegraphics[width=6.5 in]{Figures/Fig1_map.pdf}
\caption{\small{\textbf{Simplified map of Laurentia showing the location of Archean cratons and younger Paleoproterozoic and Mesoproterozoic crust (simplified from \cite{Whitmeyer2007a}. The localities from which the compiled Precambrian paleomagnetic poles were developed are shown and colored by age.}}}
\label{fig:Laurentia_map}
\end{figure}

>>>>

In the paleogeographic model framework of Pehrsson et al. (2015), the cratonic and terrane collisions leading up to the Trans-Hudson orogeny mark the initial phase of assembly of the supercontinent Nuna. The Trans-Hudson orogeny itself is taken to be the terminal collision associated with the closure of the Manikewan Ocean that had previous been a large oceanic tract separating the Superior craton from the composite Slave+Rae+Hearne+Nain cratons (often referred to as the Churchill domain or plate; e.g. Skipton et al., 2016; Weller and St-Onge, 2017). This model posits that this period terminal collision is not only associated with the amalgmation of Laurentia, but is also associated with the assembly of the supercontinent Nuna that including other major Paleoproterozoic cratons including Siberia, Congo/Sao Francisco, West Africa, and Amazonia (Pehrsson et al., 2015). Following the Trans-Hudson orogeny, the locus of orogenesis migrated to the exterior of Laurentia. This change marks a change in the style of Laurentia's growth as subsequent growth proceeding dominantly through accretion of juvenile crust along the southern and eastern margin of the nucleus of Archean cratons (\citealp{Whitmeyer2007a}; \ref{fig:Laurentia_map}).

@@

\begin{figure}
\centering
\includegraphics[width=6.5 in]{Figures/Fig1_map.pdf}
\caption{\small{\textbf{Simplified map of Laurentia showing the location of Archean cratons (labeled with text) and younger Paleoproterozoic and Mesoproterozoic crust (simplified from \cite{Whitmeyer2007a}. The localities from which the compiled Precambrian paleomagnetic poles were developed are shown and colored by age.}}}
\label{fig:Laurentia_map}
\end{figure}
